\chapter{Results and Evaluation}

\section{Tests and validation}
\subsection{Functional validation}
Manual and automated checks of authentication flows, chat endpoint contracts, and conversation listing scoped per user.

\subsection{Conversational behavior validation}
Scenarios for greetings, KPI queries, missing period prompts, follow-up messages, and quick actions (change granularity, shift year).

\subsection{KPI and graphical visualization testing}
Validation of scalar JSON, category/value tables, and \texttt{\{period, value\}} series rendered as charts.

\subsection{RBAC and security testing}
Attempts to query unauthorized years must return access denied without blocking general chat.

\subsection{Azure SQL compatibility testing}
Regression runs of translated SQL against Azure objects and drivers.

\subsection{Speech-to-text validation}
Optional browser-dependent checks.

\section{Discussion}
\subsection{Solution analysis}
The system meets the objective of combining conversational access with deterministic KPI computation for industrial use. The hybrid pipeline reduces uncontrolled generative risk while preserving UX.

\subsection{Comparison with existing approaches}
Compared with traditional BI dashboards, the assistant improves accessibility; compared with LLM-only chat, it improves numeric reliability through SQL-first processing and RBAC.

\subsection{User feedback (thumbs up / down)}
Binary feedback creates an auditable corpus for quality improvement and feeds retrieval of past negative ratings into contextualization to avoid repeating similar mistakes.

\subsection{Limitations and challenges}
Binary feedback lacks structured error categories; LLM fallback paths require ongoing guardrail testing; SSO and cookie policies vary by browser; maintenance of KPI rules grows with schema evolution.
